---
title: "Unix Shell"
output:
  learnr::tutorial:
    progressive: true
    allow_skip: true
runtime: shiny_prerendered
description: "Learn the basics of the Unix shell"
---

<!--
-->

```{r setup, include=FALSE}
library(learnr)
library(RCurl)
```

### Instructions

* Watch the following videos and answer the accompanying questions:
  * Introducing the shell
  * Navigating files and directories
  * Working with files and directories
  * Pipes and filters

  
### Problems

#### [Navigating Files and Directories](https://swcarpentry.github.io/shell-novice/instructor/02-filedir.html)


```{r q1_1, echo=FALSE}
question_text("You can also use two options at the same time. What does the command `ls` do when used with the `-l` option? What about if you use both the `-l` and the `-h` option? Some of its output is about properties that we do not cover in this lesson (such as file permissions and ownership), but the rest should be useful nevertheless.",
              answer_fn(function(value){
                correct("This will be graded by hand after completion of the tutorial.")
                }))
```


```{r q1_2, echo=FALSE}
question_text("By default, `ls` lists the contents of a directory in alphabetical order by name. The command `ls -t` lists items by time of last change instead of alphabetically. The command `ls -r` lists the contents of a directory in reverse order. Which file is displayed last when you combine the `-t` and `-r` options? Hint: You may need to use the `-l` option to see the last changed dates.",
              answer_fn(function(value){
                correct("This will be graded by hand after completion of the tutorial.")
                }))
```


```{r q1_3, echo=FALSE}
question("Starting from `/Users/nelle/data`, which of the following commands could Nelle use to navigate to her home directory, which is `/Users/nelle`?",
         answer("cd .", message = "This will take you to the current directory."),
         answer("cd /", message = "This will take you to the root directory."),
         answer("cd /home/nelle", message = "This will take you to the /home/nelle directory."),
         answer("cd ../.." , message = "This will take you up two directories."),
         answer("cd ~", correct = TRUE),
         answer("cd home", message = "This will take you to /Users/nelle/data/home/ (if it exists)."),
         answer("cd ~/data/..", correct = TRUE),
         answer("cd", correct = TRUE),
         answer("cd ..", correct = TRUE),
         allow_retry = TRUE)
```

```{r q1_4, echo=FALSE}
question("Using the filesystem diagram below, if `pwd` displays `/Users/thing`, what will `ls -F ../backup` display?",
         answer("`../backup: No such file or directory`"),
         answer("`2012-12-01 2013-01-08 2013-01-27`", message = "This would be the result for `ls backup`"),
         answer("`2012-12-01/ 2013-01-08/ 2013-01-27/`", message = "This would be the result for `ls -F backup`"),
         answer("`original/ pnas_final/ pnas_sub/`", correct = TRUE),
         allow_retry = TRUE)
```

![](https://swcarpentry.github.io/shell-novice/fig/filesystem-challenge.svg)

```{r q1_5, echo=FALSE}
question("Using the same filesystem diagram as above, if `pwd` displays `/Users/backup`, and `-r` tells `ls` to display things in reverse order, what command(s) will result in the following output: `pnas_sub/ pnas_final/ original/`",
         answer("`ls pwd`", message = "This would return an error: `ls: pwd: No such file or directory`."),
         answer("`ls -r -F`", correct = TRUE),
         answer("`ls -r -F /Users/backup`", correct = TRUE),
         allow_retry = TRUE)
```


#### [Working with Files and Directories](https://swcarpentry.github.io/shell-novice/instructor/03-create.html)

We have seen how to create text files using the `nano` editor. Now, try the following command: `touch my_file.txt`

```{r q2_1a, echo=FALSE}
question_text("What did the `touch` command do? When you look at your current directory using the GUI file explorer, does the file show up?",
              answer_fn(function(value){
                correct("This will be graded by hand after completion of the tutorial.")
              }))
```

```{r q2_1b, echo=FALSE}
question_text("Use `ls -l` to inspect the files. How large is `my_file.txt`",
              answer("0", correct = TRUE),
              answer("0B", correct = TRUE),
              allow_retry = TRUE)
```

```{r q2_1c, echo=FALSE}
question_text("When might you want to create a file this way?",
              answer_fn(function(value){
                correct("This will be graded by hand after completion of the tutorial.")
              }))
```

```{r q2_2, echo=FALSE}
question_text("After running the commands below, Jamie realizes that she put the files `sucrose.dat` and `maltose.dat` into the wrong folder. The files should have been placed in the `raw` folder. Fill in the blanks to move these files to the `raw` folder (i.e. the one she forgot to put them in): `mv sucrose.dat maltose.dat ____/____`",
              answer("mv sucrose.dat maltose.dat ../raw", correct = TRUE),
              answer('../raw', correct = TRUE),
              answer('.. raw', correct = TRUE),
              allow_retry = TRUE)
```

```
$ ls -F
 analyzed/ raw/
 
$ ls -F analyzed
fructose.dat glucose.dat maltose.dat sucrose.dat

$ cd analyzed
```

```{r q2_3, echo=FALSE}
question("Suppose that you created a plain-text file in your current directory to contain a list of the statistical tests you will need to do to analyze your data, and named it `statstics.txt`. After creating and saving this file you realize you misspelled the file name! You want to correct the mistake, which of the following commands could you use to do so?",
         answer("`cp statstics.txt statistics.txt`", message= "This would copy the file, not rename it."),
         answer("`mv statstics.txt statistics.txt`", correct = TRUE),
         answer("`mv statstics.txt .`", message = "This would move the file to the current directory (doing nothing)."),
         answer("`cp statstics.txt .`", message = "This would copy the file to the current directory (doing nothing)."),
         allow_retry = TRUE)
```

```{r q2_4, echo=FALSE}
question("What is the output of the closing `ls` command in the sequence shown below?",
         answer("`proteins-saved.dat recombined`", message = "The second argument of the copy (`../proteins-saved.dat`) is relative to the current working directory, so it would be copied one directory above where we are currently at."),
         answer("`recombined`", correct = TRUE),
         answer("`proteins.dat recombined`", message = "This is what we would get if we hadn't moved the file into `recombined/`."),
         answer("`proteins-saved.dat`"),
         allow_retry = TRUE)

```

```
$ pwd
/Users/jamie/data

$ ls
proteins.dat

$ mkdir recombined

$ mv proteins.dat recombined/

$ cp recombined/proteins.dat ../proteins-saved.dat

$ ls
```

```{r q2_5, echo=FALSE}
question_text("What happens when we execute `rm -i thesis_backup/quotations.txt`? Why would we want this protection when using `rm`?",
              answer_fn(function(value){
                correct("This will be graded by hand after completion of the tutorial.")
              }))
```

For the following exercises, you can test the commands in the `shell-lesson-data/exercise-data` directory.

```{r q2_6a, echo=FALSE}
question_text("In the example below, what does `cp` do when given several file names and a directory name?",
              answer_fn(function(value){
                correct("This will be graded by hand after completion of the tutorial.")
              }))
```

```
$ mkdir backup

$ cp creatures/minotaur.dat creatures/unicorn.dat backup/
```

```{r q2_6b, echo=FALSE}
question_text("In the example below, what does `cp` do when given three or more file names?",
              answer_fn(function(value){
                correct("This will be graded by hand after completion of the tutorial.")
              }))
```

```
$ cd creatures

$ ls -F
basilisk.dat  minotaur.dat  unicorn.dat

$ cp minotaur.dat unicorn.dat basilisk.dat
```

```{r q2_7, echo=FALSE}
question("When run in the `alkanes` directory, which ls command(s) will produce this output? `ethane.pdb methane.pdb`",
         answer("`ls *t*ane.pdb`", message = "This shows all files whose names contain zero or more characters (*) followed by the letter t, then zero or more characters (*) followed by ane.pdb. This gives ethane.pdb methane.pdb octane.pdb pentane.pdb."),
         answer("`ls *t?ne.*`", message = "This shows all files whose names start with zero or more characters (*) followed by the letter t, then a single character (?), then ne. followed by zero or more characters (*). This will give us octane.pdb and pentane.pdb but doesn’t match anything which ends in thane.pdb."),
         answer("`ls *t??ne.pdb`", correct = TRUE),
         answer("`ls ethane.*`", message = "This will only show `ethane.`."),
         allow_retry = TRUE)
```


You’re starting a new experiment and would like to duplicate the directory structure from your previous experiment so you can add new data.

Assume that the previous experiment is in a folder called `2016-05-18`, which contains a data folder that in turn contains folders named raw and processed that contain data files. The goal is to copy the folder structure of the `2016-05-18` folder into a folder called `2016-05-20` so that your final directory structure looks like this:

```
2016-05-20/
└── data
   ├── processed
   └── raw
```

```{r q2_8, echo=FALSE}
question("Which of the following set of commands would achieve this objective?",
         answer(paste("```",
                      "$ mkdir 2016-05-20",
                      "$ mkdir 2016-05-20/data",
                      "$ mkdir 2016-05-20/data/processed",
                      "$ mkdir 2016-05-20/data/raw", 
                      "```", sep = '\n'), correct = TRUE),
         answer(paste("```",
                      "$ mkdir 2016-05-20",
                      "$ cd 2016-05-20",
                      "$ mkdir data",
                      "$ cd data",
                      "$ mkdir raw processed",
                      "```", sep = '\n'), correct = TRUE),
         answer(paste("```",
                      "$ mkdir 2016-05-20/data/raw",
                      "$ mkdir 2016-05-20/data/processed",
                      "```", sep = '\n'), message = "This would throw an error: `mkdir: 2016-05-20/data: No such file or directory`"),
         answer(paste("```",
                      "$ mkdir -p 2016-05-20/data/raw",
                      "$ mkdir -p 2016-05-20/data/processed",
                      "```", sep = '\n'), correct = TRUE),
         answer(paste("```",
                      "$ mkdir 2016-05-20",
                      "$ cd 2016-05-20",
                      "$ mkdir data",
                      "$ mkdir raw processed",
                      "```", sep = '\n'), message = "This would put `raw` and `processed` in `2016-05-20` with `data`."),
         allow_retry = TRUE)
```


```{r submit, echo=FALSE}
# see https://stackoverflow.com/questions/76888127/how-do-i-count-the-correct-answers-in-an-interactive-quiz-in-learnr
question_text("When you are finished, enter your name and click `Submit Answer` to submit your work for grading.",
              answer_fn(function(value){
                
                googleFormID <- "1FAIpQLSfXcLDEfkuCzIjqg1IPDKNAh-a_dRSDh3rrrNL7PvTzEbMLqg"
                googleFormFieldID <- "entry.503480725"
                
                state <- shiny::getDefaultReactiveDomain() |>
                  learnr:::get_objects() |>
                  deparse() |>
                  paste(collapse = ' ') |>
                  gsub(pattern = 'list(list(',
                       replacement = 'list(list(assignment="UnixShell", ',
                       fixed = TRUE)
                
                names(state)[1] <- googleFormFieldID

                postForm(paste0("https://docs.google.com/forms/d/e/",
                                googleFormID,
                                "/formResponse"), 
                         .params = state)
                
                correct('Thank you. Your work has been submitted for grading.')
                }))
```
